---
title: "Text analysis Task3"
author: "Yuli Jin"
date: "2021/11/24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=F,message = F,echo=F,highlight=F)
#knitr::opts_chunk$set(echo = TRUE,out.width="0.9\\linewidth",dev="png",fig.align  = 'center')
knitr::opts_chunk$set(fig.width=6, fig.height=4,fig.align = "center") 
pacman::p_load(
tidyverse,
magrittr,
knitr,
gutenbergr,
tidytext,
sentimentr
)



```



```{r}
# gutenberg_metadata
# gutenberg_works(str_detect(author, "Zweig")) #find author's book 
my_book=gutenberg_download(c(45755)) # download the book
#write.table(my_book,'testbook2.txt',row.names = F)
```

```{r}
# this chunk is used to set tnum database and source the function
library(tnum)
tnum.authorize("mssp1.bu.edu")
tnum.setSpace("test2")
source("Book2TN-v6A-1.R")

```

```{r}
#This chunk is used to put my book into tnum
#mybook<-read_lines('testbook.txt')
mybook<-read.table('testbookv2.txt',header = T)
#tnBooksFromLines(mybook$text, "Zweig/test2")
```


```{r}
# creat tidy book:
# linenumber is used to get row number_of_photo_plot
# chapter is used to find chapter cunsum get the chapter number

tidy_books <- my_book %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>%
  unnest_tokens(word, text)
```



## task 3 sentence-level analysis

### tnum

First, I put the book into tnum, the following table shows evidence of my tnum database.

```{r echo=T}
# query heading text to display the head
q24<- tnum.query('zweig/test2/heading# has text',max=90)
df24 <- tnum.objectsToDf(q24) # turn the object to df
knitr::kable(df24 %>% select(subject:numeric.value)%>% head())
```


```{r echo=T}
# query section and heading text to display the head
q26<- tnum.query('zweig/test2# has text',max=60)
df26 <- tnum.objectsToDf(q26) # turn the object to df
df26 %>% select(subject:string.value)%>% head()

```

Then I use sentimentr to get sentiment score group by these scores with section to get the average result. The plot sort the average sentiment score from high to low.

```{r}
# query section text
df27<- tnum.query('zweig/test2/section# has text',max=7000) %>% tnum.objectsToDf()
#df27 %>% view()
# separate the subject
book_sentence<-df27 %>% separate(col=subject,
                  into = c("path1", "path2","section","paragraph","sentence"), 
                  sep = "/", 
                  fill = "right") %>% 
  select(section:string.value)

#detect the section paragraoh and sentence number and convert it from character into numeric
book_sentence<-book_sentence %>% mutate_at(c('section','paragraph','sentence'),~str_extract_all(.,"\\d+") %>% unlist() %>% as.numeric())
# use sentimentr to get sentiment score group by these scores with section to get the average result
sentence_out<-book_sentence %>% dplyr::mutate(sentence_split = get_sentences(string.value))%$%
    sentiment_by(sentence_split, list(section))

plot(sentence_out)

```

### Compare this analysis with the analysis you did in Task TWO

It is difficult to directly compare Sentimentr and Bing's score. Therefore, I apply `scale` function to keep two variable into the same criteria. Then I use ggplot to plot bar plot. From the Figure below, we can see that the trends, say positive and negetive direction, are mainly similar. But the exact number differs from two methods. Generally, sentimentr package is more optimictic than Bing method. 

```{r fig.cap="sentiment comparison"}
# create a new bing with index=chapter
new_bing<-tidy_books %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al.") %>% 
    count(method, index = chapter, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

# scale sentiment to keep unit same 
new_bing2<-new_bing %>% mutate(bing_scale=scale(sentiment)) %>% select(method,index,bing_scale)
# change colname in order to join by section
colnames(new_bing2)[2]='section'
# scale sentiment to keep unit same 
sentence_out<-sentence_out %>% mutate(sentimentr_scale=scale(ave_sentiment))
# join two df
sentence_out_2method<-left_join(sentence_out,new_bing2,by='section')%>% select(section,bing_scale,sentimentr_scale)
# use pivot longer for ggplot
sentence_out_2method_plot<-sentence_out_2method %>% pivot_longer(cols=c('sentimentr_scale','bing_scale'),names_to = 'sentiment')
# create barplot to compare
sentence_out_2method_plot %>%ggplot(aes(y=value,x=factor(section))) +
  geom_bar(aes(fill=factor(sentiment)),stat='identity',position = "dodge",width = 0.7)+theme_bw()

```

\newpage


### EXTRA CREDIT: character analysis

Baron and Edger are two main character among the fiction book. I Pick these two characters from my book.     
The following table in the count number of times each character appears in each chapter:

```{r}
#theme(legend.key.size = unit(2, 'cm'),legend.title = element_text(size=30),legend.text = element_text(size=30))
# use regular expression to find two main characters
book_sentence_indi<-book_sentence %>% mutate(baron=str_match(book_sentence$string.value,regex('([Bb]aron)'))[,1],
                         edgar=str_match(book_sentence$string.value,regex('(Edgar)'))[,1])
# use sentiment_by to get the score
score<-book_sentence_indi %>% dplyr::mutate(sentence_split = get_sentences(string.value))%$%
    sentiment_by(sentence_split) %>% `$`(ave_sentiment)

# count two characters' time in each chapter
book_sentence_indi$score<-score
re<-book_sentence_indi %>% group_by(section) %>% summarise(baron=sum(baron %>% is.na() %>% `!`()),
                                                       edgar=sum(edgar%>% is.na() %>% `!`()))

#knitr::kable(re,'simple')
# use group by to display the result
re2<-book_sentence_indi %>% group_by(section,paragraph) %>% summarise(
  both_appear=sum(baron %>% is.na() %>% `!`() & edgar%>% is.na() %>% `!`() ))

#re2 %>% filter(both_appear>0)
#knitr::kable(re2 %>% filter(both_appear>0),'simple')
```

chapter    baron   edgar
--------  ------  ------
       1      10       2
       2      22      17
       3      18      16
       4      13      12
       5       9       5
       6      16      18
       7      12      13
       8      15      24
       9      13      19
      10       8      14
      11      10      12
      12       5      18
      13       0      11
      14       1      13
      15       1      14




The following table is the count of number of times both characters appear in the same paragraphs.


 section   paragraph   both_appear
--------  ----------  ------------
       2           4             1
       2          28             1
       2          35             1
       2          36             1
       2          40             1
       3           1             1
       3          16             1
       4           3             1
       4           7             1
       4          11             1
       4          12             1
       4          23             1
       4          28             1
       5           1             1
       6           1             1
       6           3             1
       6          21             1
       7           5             1
       7           7             1
       7           8             1
       7           9             1
       8           1             1
       8           6             1
       8          11             1
       8          29             1
       8          31             1
       8          35             1
       9           2             1
       9          21             1
       9          32             1
       9          41             1
      10          11             1
      11           5             1
      11          16             2


```{r eval=F}


tnum.getDBPathList(taxonomy="subject", levels=2)

#tnBooksFromLines(time_machine$text, "wells/hw_time_1")

q20<-tnum.query(query="zweig/test1# has *",max=100000)
df20 <- tnum.objectsToDf(q20)
df20 %>% view()
q24<- tnum.query('zweig/test1/heading# has *',max=60)
df24 <- tnum.objectsToDf(q24)
df24 %>% view()

q26<- tnum.query('zweig/test1# has text',max=6000)
df26 <- tnum.objectsToDf(q26)
df26 %>% view()


# q24<- tnum.query('wells9/hw9/heading# has *',max=6000)
# df24 <- tnum.objectsToDf(q24)
# 
# q22<-tnum.query('wells9/hw9/heading:0022# has *')
# df22<-tnum.objectsToDf(q22)
# ord_ch1 <-unlist( tnum.query('wells9/hw9/heading:0022# has ordinal') )
# ord_ch2<-unlist(tnum.query('wells9/hw9/heading:0023# has ordinal'))
# 
# q25<-tnum.query('wells9/hw9/heading:0023# has *')
# df25<-tnum.objectsToDf(q25)
#   
# ch1_txt<-tnum.query('wells9/hw9/section:0022/paragraph:0002# has text',max=30)
# ch1_txt_df<-tnum.objectsToDf(ch1_txt)
# ch1_txt_df$string.value
# 
# ch2_txt<-tnum.query('wells9/hw9/section:0022/paragraph:0002/sentence:# has *',max=30)
# 
# ch2_txt_df<-tnum.objectsToDf(ch2_txt)
# ch2_txt_df$string.value
# 
# length(ch2_txt_df$string.value)
# 
# 
# q21<-tnum.query('wells9/hw9/section:0022/paragraph:0001/# has *',max=30)
# df21<-tnum.objectsToDf(q21)
# 
# library(sentimentr)
# 
# my_book$text[105:145] %>% sentiment()
```


